\sffamily Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies

### 2017-06-22 Draft/Draft0.4.bib2.tex
minor changes

%\documentclass[preprint,prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
%\documentclass[prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
%\documentclass[aps,twocolumn,showpacs,floatfix,superscriptaddress]{revtex4}
\documentclass[prl,twocolumn,superscriptaddress,aps,amsmath,amssymb,nofootinbib,altaffilletter]{revtex4}
%\documentclass[prl,superscriptaddress,twocolumn,nopreprintnumbers,floatfix,preprintnumbers,altaffilletter]{revtex4}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{array}
\usepackage{multirow}
\usepackage{float}
\usepackage{color}
\graphicspath{{figs/}}

\begin{document}

\title{Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}

\author{ Xiao-Dong Li,$^{1,\dagger}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3,\star}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4,1}$
and Sungwook E. Hong$^{2}$}

  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea}
  \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}

\begin{abstract}
We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
allowing for competitive and unbiased constrains. 
A combination of CMB+BAO+SNIa+$H_0$+AP yields
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL).
Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
The method can be combined with the standard BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

\pacs{95.36.+x, 98.80.–k}
\maketitle

%\section{Introduction}
{\it Introduction.}---
The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing dark energy models.

@@

\begin{figure*}
   \centering{
   \includegraphics[height=5cm]{fig_xy.eps}
   %\includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
   assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
   There are four perfect squares with their true shapes plotted in blue dashed lines.
   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
   The apparently distorted shapes are plotted in red solid lines.
   }
\end{figure*}

%$\xi_{\Delta s}(\mu)\equiv \int_{s_{\rm min}}^{s_{\rm max}} xi(s,\mu) ds$
%($s$ is the clustering scale).
%The RSD effect significantly distorts the shape of $\xi_{\Delta s}(mu)$ but exhibits much less redshift evolution 
%compared to the amount of change in due to incorrectly adopted cosmologies .

%When incorrect cosmological parameters are adopted, the shape of $\xi(\mu)$
%appears anisotropic due to the AP effect, and the amplitude
%is shifted by the change in comoving volume; both effects
%have significant redshift dependence. We test the method
%using the 2pCF on mock surveys drawn from HR3 and
%find the constraints obtained are tighter than those from
%the methodology of Li et al. (2014).

@@

%The paper is organised as follows; 
%in \S\ref{sec:method} we will briefly review the {\em clustering shells} method as proposed by \citet{Li2016} 
%and then discuss some improvements that allow us to extend and generalise the analysis for any dark energy model. 
%%In \S\ref{wcdm_constraint} we perform a consistency check with our pervious work using the same SDSS DR12 galaxies 
%%and focusing on a constant dark energy e.o.s parameter, $w$. 
%The results are presented in \S\ref{sec:results}, showing the constraints on the expansion history in terms of CPL parameters, $w_0, w_a$. 
%In \S\ref{sec:test} we perform test on the robustness of our results. 
%We then conclude in \S\ref{sec:conclusion}.

%\section{Methodology}\label{sec:method}
{\it Methodology.}---

The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.

Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed
\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalise these {\em clustering shells} as 
$\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
to nullify the amplitude information of the clustering signal, 
which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.

%\section{Reproducing wCDM Constraints}\label{wcdm_constraint}
%As a first trial, we firstly try to reproduce the constraints on $\Omega_m$ and $w$ in \citep{Li2016}:
%As a first trial of reproduce the $\Omega_m-w$ constraints presented in \citep{Li2016},
%we obtains
%\begin{equation}
%\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034\ (w\rm CDM).
%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
%\end{equation}
%The results are rather insensitive to the choice of fiducial cosmology.
%while taking a different fiducial cosmology yields
%\begin{eqnarray}
%\Omega_m = 0.300 \pm 0.008,\ w=-1.057\pm 0.034\ (\rm fid:\ \Omega_m=0.26, w=-0.6),\\    
%\Omega_m = 0.301 \pm 0.009,\ w=-1.055\pm 0.039\ (\rm fid:\ \Omega_m=0.31, w=-1.0),\\
%\Omega_m = 0.302 \pm 0.008,\ w=-1.050\pm 0.035\ (\rm fid:\ \Omega_m=0.31, w=-0.6),\\
%\Omega_m = 0.301 \pm 0.009,\ w=-1.052\pm 0.038\ (\rm fid:\ \Omega_m=0.31, w=-1.4),\\
%\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034\ (\rm fid:\ \Omega_m=0.11, w=-2.0).
%\end{eqnarray}
%so the derived constraints are rather insensitive to the fiducial cosmology.
%Even when adopting an extremely unlikely fiducial cosmological model, such as $\Omega_m=0.11, w=-2.0$, 
%yields correct estimation of parameters of $\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034$.
%For consideration of safety, when using the approxmiated method we slightly reduced the number of binning in $\hat\xi_{\Delta s}(\mu)$,
%so the error bars are slightly larger than \citep{Li2016} %due to the limitation of approximation method
%\footnote{We use $n_{\mu}$=20-25, while \citep{Li2016} adopted $n_{\mu}$=25-35.
%The approximate 2pCF contour begins to be noisy if using such a large number of $n_\mu$.}.
%from the 
%The approximate 2pCF may not be accurate enough }

%Using other fiducial cosmologies we derive similar cosmological constraints...
%We simply adopt the $\Omega_m=0.26, w=-1$ as the fiducial cosmology in the following analysis...

%\section{Results}\label{sec:results}
{\it Results.}---

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=5.3cm]{fig_nbar.eps}
   \includegraphics[width=7cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.
%   Their redshift ranges are listed.                                       .
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
\footnote{http://pla.esac.esa.int/pla/\#cosmology}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of 
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To include the AP method into the constraints,
We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. After multiplying the sample likelihoods with ours, while also changing the sample weights {\bf (HOW CHANGE?)}, we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
\begin{equation}
%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
\end{equation}
%$$.
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

%\cite{Li2016} shows that the AP method outperforms SNIa in constraining the parameter space of $\Omega_m-w$.
%Similarly we find it outperforms in constraining $w_0-w_a$, as shown in the middle panel of Fig.\ref{fig_TpCF}.

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_con}
   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
   %Results are consistent with $\Lambda$CDM.
   The constrained area is significantly reduced after combined with the AP method.
   %This shows the power of the AP method in constraining dynamical dark energy.
   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
   }
\end{figure*}

In this short paper we have chosen to focus on the popular CPL parameterisation of dark energy, 
however our methodology could be used with any model of cosmic expansion history.

%%% To be written!!!
%\section{Robustness Test}\label{sec:test}
{\it Robustness Test.}---

Analysing the same DR12 BOSS data, \citet{Li2016} obtained constraints on $\Omega_m$ and $w$
\begin{equation}\label{eq:wcdm_constrain_default}
\Omega_m=0.301\pm 0.006, w=-1.054\pm 0.025.
\end{equation}
In our new ``approximate 2pCF'' approach, while taking a fiducial cosmological model of $\Omega_m=0.26, w=-1$, we obtain consistent results of,
\begin{equation}
\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034.
%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
\end{equation}
Since we use a smaller $n_{\mu}$ value than that adopted by \citep{Li2016}
\footnote{\citep{Li2016} adopted $n_{\mu}=25-35$ to achieve tighter constraints.
Since we are using an approximate 2pCF, for robustness considerations we use $n_{\mu}=20-25$.}, 
resulting in a slightly enlarged error bar. 
The central values of the parameters agree quite well, demonstrating the reliability of the approximate 2pCF method.

%\begin{figure*}
%   \centering{
%   \includegraphics[width=6cm]{figIO.eps}
%   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
%   %\includegraphics[height=8cm]{fig2b.pdf}
%   %   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%   %    \includegraphics[height=8cm]{smu.eps}
%   }
%   \caption{\label{fig_IO}
%   Input-output test of the AP method. 
%   The input cosmology (marker by green plus) is recovered at $\sim$0.5$\sigma$ 
%   using 4 realizations.
%   }
%\end{figure*}

We also performed an input-output test on four realizations of the HR4 mock catalogues \cite{hr4}.
%In the framework of $w$CDM cosmology, %Figure \ref{fig_IO} shows 
The input cosmology $\Omega_m=0.26$, $w=-1$ is recovered well, lying within the $\sim$0.5$\sigma$ CL region.

Finally, we performed a thorough test of all the possible variables in our methodology.
Figure \ref{fig_contest} shows that,
the result does not change if 
we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
decrease the number of angular bins to $n_{\mu}=15-20$,
change the range of clustering to $8-30 \rm Mpc/h$,
change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
exclude 1 or 2 high redshift bins,
or reduce the number of mocks to 1000.
%Constraints get weaker if increase $s_{\rm min}$,
%but are consistent with the original one.
%Even if we choose an extremely unrealistic fiducial cosmology, i.e. 
% $\Omega_m=0.11,\ w=-2.0$, the change in contour is still mild.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} on the systematic correction could influence on our final results.

%We measure the evolution of $\hat\xi_{\Delta s}$ in six redshift bins.
%on scales of $s_{\rm min}=6$, $s_{\rm max}=40$.
%Systematics subtracted with the help of HR4 simulation.
%Covariance matrix

\begin{figure*}
   \centering{
   \includegraphics[width=16cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the AP method. 
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from HR4 simulations, 
   and covariance estimated using 2,000 PATCHY mocks.
   When altering these options, the results remain robust (black contours).
   }
\end{figure*}

%\section{Conclusion}\label{sec:conclusion}
{\it Conclusion.}---

In \cite{Li2016} we proposed to constrain cosmological parameters via 
the redshift dependence of galaxy anisotropic clustering. 
This enables a robust Alcock-Paczynski test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ . 
Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

%By reducing the RSD effect the method enables using clustering information on scales of $s<6 \rm Mpc/h$.
%This is a major advance in extracting cosmological information on relatively small scales clustering.

%In sum, our AP method have many advantages:
%\begin{itemize}
%\item {\it It leads to very tight cosmological constraints (powerful)}. The 
% \item {\it Focusing on the redshift evolution of anisotropy it successfully overcome the problem of RSD, 
% which has long time been a limitation to the application of AP to LSS (successful).}
% In traditional approaches it is very challenging to model the RSD and enable a robust AP test.
% \item {\it It is robust against systematics (reliable)}. 
% \cite{Li2016} shows that $\hat\xi_{\Delta s}$ is insensitive to RSD or galaxy bias.
% Figure \ref{fig_con_tests} shows that the change in results is small even if we do not correct the systematics at all.
% \item {\it It is a major advance in extracting cosmological information on relatively small scales clustering (unique).} 
% Clustering of galaxies happen on all scales,
%but the size and shape of BAO ring only captures information mostly on scales of $s=100-120 {\rm Mpc/h}$.
%In the analysis of correlation function shape, people mostly use $s\gtrsim 40$ Mpc/h.
%Our AP method enters much smaller scales.
%
% \item {\it It does not require complicate modeling of non-linear structure growth and RSD (simple).}
% \item {\it It is complimentary to BAO (useful).}
% The method explores much smaller clustering scales than BAO. 
% \cite{Li2016} shows that, actually the directions of $\Omega_m-w$ contours of the two methods are orthogonal to each other.
%\end{itemize}

%While it is of essential importance to build larger experiments to 
%explore more of our Universe,
%the physical interpretation of the data is of equal importance.
%Considering our method enables {\it twice as much as before} information about the cosmic expansion history extracted from LSS data.
%This, in a way, significantly enhances the valuable data obtained from the very expensive experiments costing billions of dollars.

@@

\begin{acknowledgments}
We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.
\end{acknowledgments}

%% After the acknowledgments section, use the following syntax and the
%% \facility{} macro to list the keywords of facilities used in the research
%% for the paper.  Each keyword will be checked against the master list during
%% copy editing.  Individual instruments or configurations can be provided
%% in parentheses, after the keyword, but they will not be verified.

%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc.

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
%    McClintock, J. E.  1978, \apj, 224, 39

%Wang Q H, Lindon O, Hardle W. 
%Semiparametric regression analysis with missing response at random. 
%J Am Stat Assoc, 2004, 99: 334－345

\begin{thebibliography}{}
%\citep{Riess:1998}
%[astro-ph/0205436].

>>>>

\documentclass{natureprintstyle}
%\documentclass[12pt]{nature}

\spacing{1}
\spacing{2}
\spacing{1}

%\usepackage{epsfig,caption}
\usepackage{amsmath,amssymb}
\usepackage[applemac]{inputenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{bm}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{rotating}
\usepackage{hyperref}
%\captionsetup[figure]{labelformat=empty}
%\captionsetup[table]{labelformat=empty}

\newcommand{\gt}{$>$}
\newcommand{\diamonds}{\textsc{D\large{iamonds}}}
\usepackage{hyperref}

\let\citep\cite
\let\citet\cite

\bibliographystyle{naturemag}

\title{\sffamily Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}

\author{\sffamily 
Xiao-Dong Li,$^{1,\dagger}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3,\star}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4,1}$
and Sungwook E. Hong$^{2}$}
%Enrico Corsaro$^{1,2,3,4}$, Yueh-Ning Lee$^1$, Rafael A. Garc\'{i}a$^{1}$, Patrick Hennebelle$^1$, Savita Mathur$^{5}$, Paul G. Beck$^1$, Stephane Mathis$^1$, Dennis Stello$^{6,7}$ \& J\'er\^{o}me Bouvier$^8$}

\begin{document}
\maketitle
\let\thefootnote\relax\footnote{

\begin{affiliations}
  \item School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea
  \item Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea
  \item National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China
  \item Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea
\end{affiliations}
}

\vspace{-3.5mm}
\begin{abstract}
\sffamily
We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
allowing for competitive and unbiased constrains. 
A combination of CMB+BAO+SNIa+$H_0$+AP yields
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL).
Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
The method can be combined with the standard BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

\sffamily
{\it Introduction.}---
The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing dark energy models.

@@

@@

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of 
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To include the AP method into the constraints,
We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
measured the 2pCF in these redshift bins, 
and use a $\chi^2$ function to assess the redshift dependence.
Systematic effects are estimated via mocks made from Horizon Run 4 simulations \citep{HR4}, and subtracted when computing the $\chi^2$.
After adding the sample log-likelihoods with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
\begin{equation}
%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
\end{equation}
%$$.
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

We performed a thorough test of all the possible variables in our methodology.
Figure \ref{fig_contest} shows that,
the result does not change if change them.
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} 
on the systematic correction could influence on our final results.

In sum, \cite{Li2016} proposed to constrain cosmological parameters via 
the redshift dependence of galaxy anisotropic clustering.
This enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

@@

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}
